TGI-spine

### 2022-03-21 tgispine_hypotheses.Rmd
adding anovas to estimate required sample size, will be more informative when we have pilot data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
## Simulate results for one participant
```{r}
simulate_subj <- function(subid) {
trialN = 10
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

@@

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:30) {
  df <- simulate_subj(i)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)

```
## Simulate results for one participant
```{r}
simulate_subj <- function(subid) {
trialN = 9
conditionN = 8
ratingN = 3
df <- data.frame(matrix(ncol = 0, nrow = trialN*conditionN*ratingN))
df$id <- rep(subid,trialN*conditionN*ratingN)
df$trialn <- rep(1:trialN,conditionN*ratingN)
df$dermatome <- rep(rep(c(rep("within",trialN*2), rep("across",trialN*2)),2),ratingN)
df$cold_location <- rep(rep(c(rep("dist_rostr",trialN), rep("prox_caud", trialN)),conditionN/2),ratingN)
df$stimuli <- rep(c(rep("tgi",trialN*conditionN/2), rep("non-tgi",trialN*conditionN/2)),ratingN)
df$quality <- c(rep("cold",trialN*conditionN), rep("warm",trialN*conditionN), rep("burn",trialN*conditionN))

@@

# Simulate results for 30 participants
```{r}
df30 <- data.frame()
for (i in 1:50) {
  df <- simulate_subj(i)
  df30 <- rbind(df30,df)}
df30
```
```{r}
df30$conditionN[df$dermatome == "within" & df30$cold_location == "dist_rostr"] <- 1
df30$conditionN[df$dermatome == "within" & df30$cold_location == "prox_caud"] <- 2
df30$conditionN[df$dermatome == "across" & df30$cold_location == "dist_rostr"] <- 3
df30$conditionN[df$dermatome == "across" & df30$cold_location == "prox_caud"] <- 4
df30
```

@@

# running ANOVA on simulated data - to gain idea of effect size

```{r, echo=FALSE}
library(ez)
library(psychReport)
# burning VAS
burn_anova <- ezANOVA(
  data = df_subj[df_subj$quality == 'burn' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location, stimuli),
  return_aov = TRUE,
  detailed = TRUE
)

# warm VAS
warm_anova <- ezANOVA(
  data = df_subj[df_subj$quality == 'warm' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location, stimuli),
  return_aov = TRUE,
  detailed = TRUE
)

# cold VAS
cold_anova <- ezANOVA(
  data = df_subj[df_subj$quality == 'cold' ,]
  , dv = .(x)
  , wid = .(id)
  , within = .(dermatome, cold_location, stimuli),
  return_aov = TRUE,
  detailed = TRUE
)

```{r}
burn_anova
```
```{r}
warm_anova
```
``` {r}
cold_anova
```
